---
title: "INFO 3010 - Assignment 7"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Lingzi Hong
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1. (5pts) Read the file "2015.csv" to a dataframe. Have a statistical summary of the dataset. 
```{r}
library('tidyverse')

df <- read.csv("C:\\Users\\Sam\\Documents\\INFO3010\\Practice assignments\\2015.csv")

Happy_Dataset <- df

Happy_Dataset

```

### Q2. (5pts) Draw a plot with box plot of Happiness_Score for countries in each Region group. Write 2-3 sentences to describe your findings.
```{r}

ggplot(df, aes(x = Region, y = Happiness_Score, fill = Region)) +
  geom_boxplot() +
  stat_summary(fun = "mean", geom = "point" , shape = 8, 
               size = 10, color = "white")

# The median score in the sub saharan region is 7 

```

### Q3. (10pts) Draw a scatter plot matrix for variables: Happiness_Score, Family, Freedom, Government_Corruption. What is the relation between Happiness_Score and Government_Corruption? What is the relation between Happiness_Score and Freedom?
```{r}
pairs(~Happiness_Score+Family+Freedom+Government_Corruption,data = df,lower.panel = panel.smooth)

#The lower the happiness score the lower the levels of freedom
```


### Q4. (10pts) Build a linear regression model to predict Life_Expectancy with Hapiness_Score, GDP_per_Capita, Family and Government_Corruption. 
```{r}
df.regression <- lm(Life_Expectancy~Happiness_Score+GDP_per_Capita+Family+Government_Corruption,data=df)

summary(df.regression)
```

### Q5. (10pts) Check model details. Answer the following questions out of code box: What is the adjusted R-squared value? Is the linear relation significant? 

```{r}
#The adjusted r squared value is 0.3901, there is 39% less regression line than the mean. GDP, Happiness_Score, Family and Government corruption accounts for 39% of the variation
```

### Q6. (10pts) Draw diagnostic plots for the model in Q6. 
```{r}
par(mfrow = c(2, 2))
plot(df.regression)

```

